relauo Amicus Brief Models

### 2022-05-23 eda/paper-graphics.Rmd
updated tables for paper

```{r, results='asis'}
#read in models
forg_privacy_interactions <- readRDS("../modeling/justicemq-interactions/models/forg_privacy_interactions.rds")
forg_undue_interactions <- readRDS("../modeling/justicemq-interactions/models/forg_undue_interactions.rds")
lif_undue_interactions <- readRDS("../modeling/justicemq-interactions/models/lif_undue_interactions.rds")

stargazer(forg_privacy_interactions, forg_undue_interactions, lif_undue_interactions, title="Results", type='html',align=TRUE)
```

>>>>

```{r, results='asis'}
#read in models
forg_privacy <- readRDS("../modeling/amicus_type/models/forg_privacy.rds")
forg_privacy_interactions <- readRDS("../modeling/justicemq-interactions/models/forg_privacy_interactions.rds")
forg_undue <- readRDS("../modeling/amicus_type/models/forg_undue.rds")
forg_undue_interactions <- readRDS("../modeling/justicemq-interactions/models/forg_undue_interactions.rds")
lif_undue <- readRDS("../modeling/amicus_type/models/lif_undue.rds")
lif_undue_interactions <- readRDS("../modeling/justicemq-interactions/models/lif_undue_interactions.rds")
relauo_undue <- readRDS("../modeling/amicus_type/models/relauo_undue.rds")
relauo_undue_interactions <- readRDS("../modeling/justicemq-interactions/models/relauo_undue_interactions.rds")

stargazer(forg_privacy, forg_privacy_interactions, forg_undue, forg_undue_interactions, lif_undue, lif_undue_interactions, relauo_undue, relauo_undue_interactions,
          title="Results", type='html',align=TRUE,
          column.labels = c("Forg Privacy", "Forg Undue", 
                            "Life Undue", "Relauo Undue"))
# , covariate.labels = c("Justice Ideology", "Justice Gender", "Lower Court Decision", "Solicitor General Amicus Brief", "pfemam", "forgauf_privacy", "justicemq:forgauf_privacy", "forgauf_undue_burden", "justicemq:forgauf_undue_burden", "poppam", "lifauo_undue_burden", "justicemq:lifauo_undue_burden"))
```

# Table 3

```{r, results='asis'}
#read in models
forg_womenhealth <- readRDS("../modeling/amicus_type/models/forg_womenhealth.rds")
forg_womenhealth_interactions <- readRDS("../modeling/justicemq-interactions/models/forg_womenshealth_interactions.rds")
medauf_womenhealth <- readRDS("../modeling/amicus_type/models/medauf_womenhealth.rds")
medauf_womenhealth_interactions <- readRDS("../modeling/justicemq-interactions/models/medauf_womenshealth_interactions.rds")
forg_womenfuture <- readRDS("../modeling/amicus_type/models/forg_womenfuture.rds")
relauo_abortionregret <- readRDS("../modeling/amicus_type/models/relauo_abortionregret.rds")
forg_evidence <- readRDS("../modeling/amicus_type/models/forg_evidence.rds")
forg_evidence_interactions <- readRDS("../modeling/justicemq-interactions/models/forg_evidence_interactions.rds")
medauo_evidence <- readRDS("../modeling/amicus_type/models/medauo_evidence.rds")
medauo_evidence_interactions <- readRDS("../modeling/justicemq-interactions/models/medauo_evidence_interactions.rds")

stargazer(forg_womenhealth, forg_womenhealth_interactions, medauf_womenhealth, medauf_womenhealth_interactions, forg_womenfuture, relauo_abortionregret, forg_evidence, forg_evidence_interactions, medauo_evidence, medauo_evidence_interactions
          ,title="Results", type='html',align=TRUE,
          column.labels = c("Forg Privacy", "Forg Undue", 
                            "Life Undue", "Relauo Undue"))
```

# Table 4

```{r, results='asis'}
#read in models
forg_fetus <- readRDS("../modeling/amicus_type/models/forg_fetus.rds")
forg_morality <- readRDS("../modeling/amicus_type/models/forg_morality.rds")
relauo_fetus <- readRDS("../modeling/amicus_type/models/relauo_fetus.rds")
relauo_fetus_interactions <- readRDS("../modeling/justicemq-interactions/models/relauo_fetus_interactions.rds")
medauo_morality <- readRDS("../modeling/amicus_type/models/medauo_morality.rds")

stargazer(forg_fetus, forg_morality, relauo_fetus, relauo_fetus_interactions, medauo_morality
          ,title="Results", type='html',align=TRUE,
          column.labels = c("Forg Privacy", "Forg Undue", 
                            "Life Undue", "Relauo Undue"))
```

### 2022-05-23 modeling/amicus_type/forgauf.Rmd
updated tables for paper

>>>>

```{r, eval=F}
#save models for paper tables
saveRDS(mod9, "models/forg_evidence.rds")
saveRDS(mod11, "models/forg_fetus.rds")
saveRDS(mod14, "models/forg_morality.rds")
saveRDS(mod18, "models/forg_privacy.rds")
saveRDS(mod23, "models/forg_undue.rds")
saveRDS(mod25, "models/forg_womenfuture.rds")
saveRDS(mod26, "models/forg_womenhealth.rds")

```

### 2022-05-23 modeling/amicus_type/medauo.Rmd
updated women's future frame
updated tables for paper

* 0:
* 0.01:
* 0.05: morality & religion (-)
* 0.10: abortion regret (+)
* 0.20: undue burden (-), women's health (+)

@@

>>>>

* 0:
* 0.01:
* 0.05: morality & religion (-)
* 0.10: abortion regret (+), women's future life (+)
* 0.20: undue burden (-), women's health (+)

@@

```{r, eval=F}
#save models for paper tables
saveRDS(mod14, "models/medauo_morality.rds")
saveRDS(mod9, "models/medauo_evidence.rds")

```

### 2022-05-23 modeling/amicus_type/relauo.Rmd
updated women's future frame
updated tables for paper

* 0:
* 0.01:
* 0.05: abortion regret (+)
* 0.10: evidence (+)
* 0.20: bad law (+), women's health (+)

@@

>>>>

* 0:
* 0.01:
* 0.05: abortion regret (+)
* 0.10: evidence (+), women's futures (+)
* 0.20: bad law (+), women's health (+)

@@

```{r, eval=F}
#save models for paper tables
saveRDS(mod11, "models/relauo_fetus.rds")
saveRDS(mod23, "models/relauo_undue.rds")
saveRDS(mod26, "models/relauo_abortionregret.rds")

```
